### 2016-10-06 ms/ms.tex
marilia made small litte changes in the tex file after Paulos comments

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for system-level
  conservation biology. Using a long-term data set comprising nearly
  20,000 pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing assembly to be punctuated
  by significant reorganizations of interactions. In contrast, the
  non-assembling networks did not restructure as frequently. Across
  all communities, Pollinator species were opportunistic in the
  flowers they visited. Indeed, the most persistent and generalized
  species were also the most variable in their network positions. High
  species and interaction turnover was ubiquitous across assembling
  and non-assembling communities, though unique interactions turnover
  at higher rates in assembling hedgerows as the networks continually
  reorganize. Nestedness of assembling networks also increased through
  time, but there was no increase in robustness to simulated plant
  extinctions. Our results elucidate some of the mechanisms underlying
  plant-pollinator network assembly and restoration, while providing
  further evidence that hedgerows are a valuable tool for promoting
  species conservation and ecosystem provision in agricultural areas.
\end{abstract}

@@

We calculate species persistence as the proportion of surveys in which
a plant or pollinator is observed. Species observed consistently
within and between years are thus maximally persistent. Weighted
species degree is calculated from interaction observations from an
extensive dataset from Yolo County (approx.~18000 interaction records)
that included both the data included in this study and additional data
from sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness centrality \citep{freeman1978centrality} at each
site through time. Closeness centrality describes the centrality of a
species in the network by calculating path lengths to other vertices
(species) in the graph \citep{freeman1978centrality}. We use linear
mixed models to test whether the species closeness variability (log)
is related to the persistence or degree of that species \citep{lme4,
  lmetest}. We included random effects for species, as well as
site. Because the degree and persistence of pollinators were strongly
correlated, ($\rho = 0.84$, $p$-value $<$ $2*10^{-16}$), we include
each explanatory variable in the model separately. Plant degree and
persistence were not significantly correlated, but we use the same
models as we did for the pollinators for consistency. An approximately
logarithmic increase in closeness centrality, as would be expected
with assembly by preferential attachment, would also lead to a high
variability in closeness scores, so we test whether log closeness
centrality increases through time.

>>>>

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for system-level
  conservation biology. Using a long-term data set comprising nearly
  20,000 pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing assembly to be punctuated
  by significant reorganizations of interactions. In contrast, the
  non-assembling networks did not restructure as frequently. Across
  all communities, pollinator species were opportunistic in the
  flowers they visited. Indeed, the most persistent and generalized
  species were also the most variable in their network positions. High
  species and interaction turnover was ubiquitous across assembling
  and non-assembling communities, though unique interactions turnover
  at higher rates in assembling hedgerows as the networks continually
  reorganize. Nestedness of assembling networks also increased through
  time, but there was no increase in robustness to simulated plant
  extinctions. Our results elucidate some of the mechanisms underlying
  plant-pollinator network assembly and restoration, while providing
  further evidence that hedgerows are a valuable tool for promoting
  species conservation and ecosystem provision in agricultural areas.
\end{abstract}

@@

We calculate species persistence as the proportion of surveys in which
a plant or pollinator is observed. Species observed consistently
within and between years are thus maximally persistent. Weighted
species degree is calculated from interaction observations from an
extensive dataset from Yolo County (approx.~18000 interaction records)
that included both the data included in this study and additional data
from sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness centrality \citep{freeman1978centrality} at each
site through time. Closeness centrality describes the centrality of a
species in the network by calculating path lengths to other vertices
(species) in the graph \citep{freeman1978centrality}. The smaller the mean path length of a species to other species, the closer they are, and the greater the species' centrality. We use linear
mixed models to test whether the species closeness variability (log)
is related to the persistence or degree of that species \citep{lme4,
  lmetest}. We included random effects for species, as well as
site. Because the degree and persistence of pollinators were strongly
correlated, ($\rho = 0.84$, $p$-value $<$ $2*10^{-16}$), we include
each explanatory variable in the model separately. Plant degree and
persistence were not significantly correlated, but we use the same
models as we did for the pollinators for consistency. An approximately
logarithmic increase in closeness centrality, as would be expected
with assembly by preferential attachment, would also lead to a high
variability in closeness scores, so we test whether log closeness
centrality increases through time.
